### 2025-06-22 conteudo/methods/methods.tex
update number of students on the tesis

Of the students who chose to work on the ArKanjo-related tasks, 25 (20 undergraduate and 5 graduate) 
formed 11 groups to pursue the first alternative. One graduate student opted for the second alternative, 
forming a single group. Notably, none of these students had prior experience contributing to the 
Linux kernel, making this their first attempt to submit a patch as newcomers.

>>>>

Of the students who chose to work on the ArKanjo-related tasks, 26 (19 undergraduate and 7 graduate) 
formed 11 groups to pursue the first alternative. One graduate student opted for the second alternative, 
forming a single group. Notably, none of these students had prior experience contributing to the 
Linux kernel, making this their first attempt to submit a patch as newcomers.
